---
title: "Biobase"
#author: "Darren Kidney"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
#  html_document:
#    toc: true
#    theme: readable
#    highlight: tango
#    keep_md: true
#    lang: "en-GB"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "..")
  })
---

```{r knitr-setup, echo=FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = '#',
	message = FALSE,
	strip.white = TRUE
)
library(conflicted)
```

```{r}
suppressPackageStartupMessages({
	library(Biobase)
})
```

## general

```{r, eval=FALSE}
openVignette(1) # An introduction to Biobase and ExpressionSets
openVignette(2) # esApply Introduction
openVignette(3) # Notes for eSet developers
openVignette(4) # Using the reshape function
openVignette(5) # Sweave User Manual
```

## `ExpressionSet` class

Contains three matrices

1. expression data for multiple 'features' (typically genes) across multiple 'samples' (typically individuals)
1. feature-level covariates (e.g. ?)
1. sample-level covariates (e.g. age, gender)

```{r}
data(sample.ExpressionSet)
example = updateObject(sample.ExpressionSet)
validObject(example)
example
```

```{r}
class(example)
isS4(example)
getClass("ExpressionSet") # can also use showClass
#findMethods("ExpressionSet") # getMethods is deprecated
```

```{r}
experimentData(example)
abstract(example)
slotNames(example)
```

### `exprs` and `se.exprs`

Access the expression and error measurements of assay data.

* rows = 'features' - e.g. genes
* columns = samples

```{r}
class(exprs(example))
dim(exprs(example))
exprs(example)[1:5, 1:5]
```

But no `exprs.se` method for this class:

```{r}
try(class(se.exprs(example)))
```

Find help on `exprs`: 

```{r, eval=FALSE}
showMethods("exprs") # list all available methods
method?"exprs,ExpressionSet" # help on specific method
?"exprs,ExpressionSet-method" # alternative way to get help on specific method
getMethod("exprs", "ExpressionSet") # function definition for specific method
```

The `assayData` method is similar to `exprs` but returns a named list or environment containing one or more matrices of equal dimension.

```{r}
class(assayData(example))
ls(envir = assayData(example))
```

```{r}
class(assayData(example)$exprs)
dim(assayData(example)$exprs)
assayData(example)$exprs[1:5, 1:5]
```

```{r}
class(assayData(example)$se.exprs)
dim(assayData(example)$se.exprs)
assayData(example)$se.exprs[1:5, 1:5]
```

### `pData`

Access the phenotypic data (e.g., covariates) and meta-data (e.g., descriptions of covariates).

* rows = samples
* columns = sample-level variables

```{r}
class(pData(example))
dim(pData(example))
pData(example)[1:5, ]
```

```{r}
nrow(pData(example)) == ncol(exprs(example))
```

```{r}
showMethods("pData")
```

The `phenoData` method is similar to `pData` but returns an `AnnotatedDataFrame`.

```{r}
class(phenoData(example))
dim(phenoData(example))
phenoData(example)[1:5, ]
```

### `fData`

Access feature data (experiment specific information about features) and feature meta-data (e.g., descriptions of feature covariates).

* rows = features
* columns = feature-level variables

* `fData()` returns a `data.frame`  
* `featureData()` returns a `DataFrame`  

```{r}
class(fData(example))
dim(fData(example))
```

```{r}
nrow(fData(example)) == nrow(exprs(example))
```

```{r}
showMethods("fData")
```

The `featureData` method is similar to `fData` but returns an `AnnotatedDataFrame`.

```{r}
class(featureData(example))
dim(featureData(example))
```

### subsetting

```{r}
head(featureNames(example))
head(sampleNames(example))
```

```{r}
example_subset1 = example[1:5, 1:3]
dim(exprs(example_subset1))
dim(pData(example_subset1))
dim(fData(example_subset1))
```

```{r}
example_subset2 = example[featureNames(example)[1:5], sampleNames(example)[1:3]]
dim(exprs(example_subset2))
dim(pData(example_subset2))
dim(fData(example_subset2))
```

Subset by `pData` covariates

```{r}
example$sex
example$type
example$score
```

```{r}
# samples with above-average 'score' in phenoData
example_subset3 = example[, example$score > mean(example$score)]
dim(exprs(example_subset3))
dim(pData(example_subset3))
dim(fData(example_subset3))
```

### coercion

```{r}
as.data.frame(example_subset1)
```

## `AnnotatedDataFrame` class

*TODO*

## session info 

```{r}
packageVersion("BiocVersion")
sessionInfo()
```


