---
title: rlang
editor_options: 
  chunk_output_type: console
---

```{css css_custom, code=readLines("_css_custom.css"), include=FALSE}
```
```{r knitr_config, code=readLines("_knitr_config.R"), include=FALSE}
```
```{r, include=FALSE}
library(rlang)
```

*********************************************************************

* https://rlang.r-lib.org/index.html (package)  
* https://adv-r.hadley.nz/evaluation.html (advanced r chapter)  
* https://adv-r.hadley.nz/quasiquotation.html (advanced r chapter)  
* https://tidyeval.tidyverse.org/ (book)  
* https://www.rstudio.com/resources/webinars/tidy-eval/ (rstudio video)  
* https://www.youtube.com/watch?v=nERXS3ssntw (Hadley video)  
* https://dplyr.tidyverse.org/articles/programming.html  
* https://www.tidyverse.org/articles/2018/07/ggplot2-tidy-evaluation/  
* https://edwinth.github.io/blog/dplyr-recipes/  
* https://www.mango-solutions.com/blog/what-is-tidy-eval-and-why-should-i-care  

*********************************************************************

## evaluation

### expr(s) / enexpr(s)

#### expr(s)

* capture expressions that you supply
* quote contents  

```{r}
z = expr(x + y)
z
class(z)
```

```{r}
z = exprs(x + y, a + b)
z
class(z)
```

#### enexpr(s)

* capture expressions that your user supplied
* call from within a function  
* quote what the user passed to an argument  

```{r}
f = function(x){
    enexpr(x)
}
z = f(x + y)
z
class(z)
```

```{r}
f = function(x, y){
    enexprs(x, y)
}
z = f(x + y, a + b)
z
class(z)
```

### quo(s) / enquo(s)

#### quo(s)

* quote contents as a quosure

```{r}
z = quo(x + y)
z
class(z)
```

```{r}
z = quos(x + y, a + b)
z
class(z)
```

#### enquo(s)

* call from within a function  
* quote what the user passed to an argument as a quosure  

```{r}
f = function(x){
    enquo(x)
}
z = f(x + y)
z
class(z)
```

```{r}
f = function(x, y){
    enquos(x, y)
}
z = f(x + y, a + b)
z
class(z)
```

### sym(s) / ensym(s)

#### sym(s)

* convert a string to a symbol  

```{r}
z = sym("x")
z
class(z)
```

* convert a list of strings to a list of symbols  

```{r}
z = syms(list("x", "y"))
z
class(z)
```

#### ensym(s)

* call from within a function  
* quote what the user passed to an argument as a symbol  
* accepts strings  

*TODO*

### examples

```{r}
what <- "bonjour"
expr(say(what))
expr(say(!!what))
```

```{r}
what <- sym("bonjour")
expr(say(what))
expr(say(!!what))
```

*********************************************************************

## environments

Functions that create / modify enironments

base | rlang | description
------------- | ------------- | -------------
assign | env_bind | 
delayedAssign | env_bind_lazy | 
makeActiveBinding | env_bind_active | 
new.env | env | 
rm | env_unbind | 

Functions that interact with enironments

base | rlang | description
------------- | ------------- | -------------
exists | env_has | 
get | env_get | 
names | env_names | 

Functions that return enironments

base | rlang | description
------------- | ------------- | -------------
baseenv | base_env | the base environment
emptyenv | empty_env | the empty environment
environment | current_env | the current environment
globalenv | global_env | the global environment
parent.env | env_parent | the parent environment
parent.frame | caller_env | the calling environment

`sys` functions

base | rlang | description
------------- | ------------- | -------------
sys.frame |  | the calling environment
sys.frames |  |
sys.nframe |  |
sys.parent |  |
sys.parents |  |

```{r}
f = function(){
  function(){
    list(
      base = list(
        environment = environment(),
        parent.env = parent.env(environment()),
        parent.frame = parent.frame()
      ),
      rlang = list(
        current_env = current_env(),
        env_parent = env_parent(),
        caller_env = caller_env()
      ),
      sys = list(
        sys.frame = sys.frame(),
        # sys.frames = sys.frames(),
        sys.nframe = sys.nframe(),
        sys.parent = sys.parent()
        # sys.parents = sys.parents()
      )
    )
  }
}
g = f()
g()
```


*********************************************************************

## terminology

*TODO*

### frames

* elements of the call stack  
* i.e. the execution context  
* the position of a frame in the call stack is represented by an integer starting at 0 for the global environment

### quasiquotation

the combination of quotation and unquotation

### quotation

### symbol

### unquotation


