---
title: rlang
---

```{css css_custom, code=readLines("_css_custom.css"), include=FALSE}
```
```{r knitr_config, code=readLines("_knitr_config.R"), include=FALSE}
```
```{r, include=FALSE}
library(rlang)
```

*********************************************************************

* https://rlang.r-lib.org/index.html (package)  
* https://adv-r.hadley.nz/evaluation.html (advanced r chapter)  
* https://adv-r.hadley.nz/quasiquotation.html (advanced r chapter)  
* https://tidyeval.tidyverse.org/ (book)  
* https://www.rstudio.com/resources/webinars/tidy-eval/ (rstudio video)  
* https://www.youtube.com/watch?v=nERXS3ssntw (Hadley video)  
* https://dplyr.tidyverse.org/articles/programming.html  
* https://www.tidyverse.org/articles/2018/07/ggplot2-tidy-evaluation/  
* https://edwinth.github.io/blog/dplyr-recipes/  
* https://www.mango-solutions.com/blog/what-is-tidy-eval-and-why-should-i-care  

*********************************************************************

## expr(s) / enexpr(s)

### expr(s)

* capture expressions that you supply
* quote contents  

```{r}
z = expr(x + y)
z
class(z)
```

```{r}
z = exprs(x + y, a + b)
z
class(z)
```

### enexpr(s)

* capture expressions that your user supplied
* call from within a function  
* quote what the user passed to an argument  

```{r}
f = function(x){
    enexpr(x)
}
z = f(x + y)
z
class(z)
```

```{r}
f = function(x, y){
    enexprs(x, y)
}
z = f(x + y, a + b)
z
class(z)
```

*********************************************************************

## quo(s) / enquo(s)

### quo(s)

* quote contents as a quosure

```{r}
z = quo(x + y)
z
class(z)
```

```{r}
z = quos(x + y, a + b)
z
class(z)
```

### enquo(s)

* call from within a function  
* quote what the user passed to an argument as a quosure  

```{r}
f = function(x){
    enquo(x)
}
z = f(x + y)
z
class(z)
```

```{r}
f = function(x, y){
    enquos(x, y)
}
z = f(x + y, a + b)
z
class(z)
```

*********************************************************************

## sym(s) / ensym(s)

### sym(s)

* convert a string to a symbol  

```{r}
z = sym("x")
z
class(z)
```

* convert a list of strings to a list of symbols  

```{r}
z = syms(list("x", "y"))
z
class(z)
```

### ensym(s)

* call from within a function  
* quote what the user passed to an argument as a symbol  
* accepts strings  

*TODO*

*********************************************************************

## examples

```{r}
what <- "bonjour"
expr(say(what))
expr(say(!!what))
```

```{r}
what <- sym("bonjour")
expr(say(what))
expr(say(!!what))
```

*********************************************************************

## terminology

*TODO*

call

environment

expression

quasiquotation - the combination of quotation and unquotation

quotation

symbol

unquotation


