---
title: tidyverse
editor_options: 
  chunk_output_type: console
---

```{css css_custom, code=readLines("_css_custom.css"), include=FALSE}
```
```{r knitr_config, code=readLines("_knitr_config.R"), include=FALSE}
```
```{r, include=FALSE}
library(tidyverse)
```

*********************************************************************

## dbplyr

### infix functions

allows you to use expressions like LIKE which does a limited form of pattern matching:

```r
mf %>% 
  filter(x %LIKE% "%foo%") %>% 
  show_query()
```

### prefix functions

Any function that dbplyr doesn’t know about will be left as is:

```r
mf %>% 
  mutate(z = FOOFIFY(x, y)) %>% 
  show_query()
```

*********************************************************************

## dplyr

### case_when

*TODO* 

### filter_all

```{r}
df = tibble(var1 = c(1, 2, 3, NA),
            var2 = c(4, NA, 6, NA),
            var3 = c(7, 8, NA, NA))
df

df %>% filter_all(any_vars(!is.na(.))) # remove rows with ALL missing
df %>% filter_all(all_vars(!is.na(.))) # remove rows with ANY missing
df %>% filter_all(any_vars(is.na(.))) # keep rows with ANY missing
df %>% filter_all(all_vars(is.na(.))) # keep rows with ALL missing

# same as
df %>% filter(!is.na(var1) | !is.na(var2) | !is.na(var3))
df %>% filter(!is.na(var1) & !is.na(var2) & !is.na(var3))
df %>% filter(is.na(var1) | is.na(var2) | is.na(var3))
df %>% filter(is.na(var1) & is.na(var2) & is.na(var3))
```


*********************************************************************

## ggplot2

### increase space between axis and label

```r
plt + 
  theme(
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))
  )
```

### rotate x axis labels by 45 degrees

```r
plt + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### position dodge with equal width bars

```r
geom_bar(position = position_dodge2(preserve = "single"))
```

### multiple plots with aligned axes
 
```r
library(gtable)
g2 <- ggplotGrob(p2)
g3 <- ggplotGrob(p3)
g <- rbind(g2, g3, size = "first")
g$widths <- unit.pmax(g2$widths, g3$widths)
grid.newpage()
grid.draw(g)
```

*********************************************************************

## forcats

*********************************************************************

## googledrive

* https://googledrive.tidyverse.org/index.html

*********************************************************************

## lubridate

* https://lubridate.tidyverse.org/index.html

*********************************************************************

## purrr

*********************************************************************

## tibble

*********************************************************************

## tidyr

### complete

*********************************************************************

## xml2


