---
title: geospatial
---

```{r knitr_config, include = FALSE}
source("_knitr_config.R")
```

*************************************************************************

## geosphere

### distVincentyEllipsoid

*************************************************************************

## mapdata

```{r, eval=FALSE}
library(mapdata)
data(worldHiresMapEnv)
```

*************************************************************************

## maps

```{r, eval=FALSE}
library(maps)
map(
  "worldHires",
  xlab = "lon",
  ylab = "lat",
  regions = "south africa",
  xlim = c(15, 34),
  ylim = c(-35, -22),
  fill = TRUE,
  col = "grey95",
  mar = c(0, 0, 0, 1)
)
```

### map.scale

*************************************************************************

## mapproj

*************************************************************************

## maptools

### readShapePoly

*************************************************************************

## mapview

### mapview

*************************************************************************

## sf

sf::st_proj_info(type = "datum")

*************************************************************************

## raster

raster
brick 
stack
writeRaster
projectExtent

system.file("external/lux.shp", package="raster")
system.file("external/rlogo.grd", package="raster")
system.file("external/test.grd", package="raster")
raster::crs()
raster::shapefile
raster::spLines
raster::spPolygons
raster::RasterLayer, RasterBrick, and RasterStack
raster::raster, brick, stack, writeRaster, projectExtent
raster::res, dim, ncol, ncell, values, hasValues, xmax, inMemory, cellStats, crop, trim, extend, shift, merge, aggregate, disaggregate, rotate, overlay, cover, calc, cut, reclassify

*************************************************************************

## ggplot2 

### map_data

Get map data from the `maps` package.

```{r}
library(ggplot2)
states <- map_data("state")
usamap <- ggplot(states, aes(x=long, y=lat, group=group)) +
 geom_polygon(fill="white", colour="black")
usamap
```

### coord_data

```{r}
usamap + coord_map("mercator")
usamap + coord_map("azequalarea")
```

### fortify


*************************************************************************

## plotly 

ggplotly()

plot_ly() 

*************************************************************************

https://www.rspatial.org/index.html
sp::geom ?
Sp, Sf, rgeos, rgdal, maps, maptools
osmdata, mapsapi
plotly, leaflet, ggmap, mapproj

projection (X) # for rasters
projectRaster(x, ...)  # for rasters
symdif, over, extract, aggregate, merge, sp::union, cover, intersect, erase, disaggregate, bind
spplot in sp and raster
rasterViz package LM
plotRGB


