---
title: "S4"
#author: "Darren Kidney"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
#  html_document:
#    toc: true
#    theme: readable
#    highlight: tango
#    keep_md: true
#    lang: "en-GB"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "..")
  })
---

```{r knitr-setup, echo=FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = '#',
	message = FALSE,
	strip.white = TRUE
)
```

## links

* https://adv-r.hadley.nz/s4.html  
* https://kasperdanielhansen.github.io/genbioconductor/html/R_S4.html  

## general

### classes 

```{r, eval=FALSE}
getClass("aClass") # print info on specific class
showClass("aClass") # same as getClass?
findMethods("aClass") # print info on all methods available for this class
```

### generics 

```{r, eval=FALSE}
getGeneric("aGeneric") # print info on specific generic
args(getGeneric("aGeneric")) # print arguments for specific generic
```

### methods

```{r, eval=FALSE}
showMethods("aGeneric") # list all available methods
method?"aGeneric,aClass" # help on specific method
?"aGeneric,aClass-method" # alternative way to get help on specific method
getMethod("aGeneric", "aClass") # method definition
selectMethod('aGeneric', 'aClass') # same as getMethod?
```

## create a new class 

Define the class:

```{r}
setClass("Person", 
  slots = c(
    name = "character", 
    age = "numeric"
  ), 
  prototype = list(
    name = NA_character_,
    age = NA_real_
  )
)
```

Make a constructor:

```{r}
Person <- function(name, age = NA) {
  age <- as.double(age)
  new("Person", name = name, age = age)
}
```

Define a `show` method:

```{r}
setMethod("show", "Person", function(object) {
  cat(is(object)[[1]], "\n",
      "  Name: ", object@name, "\n",
      "  Age:  ", object@age, "\n",
      sep = ""
  )
})
```

Define getter and setter generics for `name` and `age`:

```{r}
setGeneric("name", function(x) standardGeneric("name"))
setGeneric("name<-", function(x, value) standardGeneric("name<-"))

setGeneric("age", function(x) standardGeneric("age"))
setGeneric("age<-", function(x, value) standardGeneric("age<-"))
```

Define getter and setter methods for `name` and `age`:

```{r}
setMethod("name", "Person", function(x) x@name)
setMethod("name<-", "Person", function(x, value) {
  x@name <- value
  validObject(x)
  x
})

setMethod("age", "Person", function(x) x@age)
setMethod("age<-", "Person", function(x, value) {
  x@age <- value
  validObject(x)
  x
})
```

Write some checks (which will be performed via `validObject()`)

```{r}
setValidity("Person", function(object) {
 if (!grepl("^[A-Z]", object@name, perl = TRUE)) {
   "@name must start with a capital letter"
 } else if (!is.na(object@age) && object@age < 0) {
   "@age must be non-negative"
   TRUE
 } else {
 }
})
```

Make an instance of the class:

```{r}
(bob = Person("Bob"))
isS4(bob)
is(bob, 'Person')
validObject(bob)
```

Get and set the 'fields' (i.e. attributes):

```{r}
name(bob)
age(bob) = 42
age(bob)
bob
```

Create a new subclass using inheritance.

```{r}
setClass("Employee", 
  contains = "Person", 
  slots = c(
    boss = "Person"
  ),
  prototype = list(
    boss = new("Person")
  )
)
```

## session info

```{r}
packageVersion("BiocVersion")
sessionInfo()
```
