---
title: base R
editor_options: 
  chunk_output_type: console
---

```{css css_custom, code=readLines("_css_custom.css"), echo=FALSE}
```
```{r knitr_config, code=readLines("_knitr_config.R"), echo=FALSE}
```

*********************************************************************

## operators

### assignemt operators

* `<<-` modifies an existing variable found in the parent environment - if an existing variable isn't found, it will create one in the global environment  

### colon operators

* `::` access exported objects from package namespace  
* `:::` access exported and non-exported objects from package namespace  

In both cases, the package namespace will be loaded (if it wasn't already loaded), but the package will not be attached to the search path.

*********************************************************************

## namespaces

### attachNamespace

* loads the package namespace and registers is to an internal database  
* runs the package `.onLoad()` function  
* attaches the package namespace to the search path
* runs the package `.onAttach()` function  

### loadNamespace {#loadNamespace}

* loads the package namespace and registers is to an internal database  
* runs the package `.onLoad()` function  
* does not attach the package namespace to the search path

### requireNamespace

* just a wrapper around [loadNamespace](#loadNamespace)  
* the only difference is that it returns a logical value (FALSE if)

*********************************************************************

## match

* get a vector of positions in `y` where values match those in `x`
* returns an integer vector with length equal to length of `x`

```{r}
x = c("h", "e", "l", "l", "l", "o")
y = letters
i = match(x, y)
i
y[i]
```

* indexes correspond to the **first** match in `y`

```{r}
z = c(letters, letters)
i = match(x, z)
i
z[i]
```

*********************************************************************

## pipe

read from clipboard

```r
readr::read_tsv(pipe("pbpaste"))
```

write to clipboard

```r
my.data <- data.frame(x = c(1,1,2,3), 
                   y = c(1,1, 3, 4), 
                   z = c(1,4,6,7))
clip <- pipe("pbcopy", "w")                       
write.table(my.data, file=clip, sep = '\t', row.names = FALSE)
close(clip)
```

for Windows:

https://www.johndcook.com/blog/r_excel_clipboard/

*********************************************************************

## replace

```{r, eval=TRUE}
x = c(a = 2)
defaults = c(a = 1, b = 2)
replace(defaults, names(x), x)
```

*********************************************************************

## tryCatch

```r
tryCatch(1, finally = print("Hello"))
e <- simpleError("test error")
## Not run: 
 stop(e)
 tryCatch(stop(e), finally = print("Hello"))
 tryCatch(stop("fred"), finally = print("Hello"))

## End(Not run)
tryCatch(stop(e), error = function(e) e, finally = print("Hello"))
tryCatch(stop("fred"),  error = function(e) e, finally = print("Hello"))
```

*********************************************************************

R6

Htmltools

Stan

Plumber


