---
title: sp
---

```{css css_custom, code=readLines("_css_custom.css"), echo=FALSE}
```
```{r knitr_config, code=readLines("_knitr_config.R"), echo=FALSE}
```
```{r, include=FALSE}
knitr::opts_chunk$set(
    # fig.width = 4, 
    # fig.height = 4
)
library(sp)
```

*********************************************************************

## CRS

* Coordinate Reference System  
* defines locations on the Earth's surface  
* notation used to describe the CRS is called the `proj4string` (from the `PROJ.4` library)  
* the proj4string has several attributes, including:
  * `proj` - projection
  * `datum` - defines origin and direction of axes
  * `ellps` - model for the shape of the earth
* CRS can also be reference by an EPSG code (European Petroleum Survey Group) 

### Geographic / unprojected

Latitude/longitde for referencing location on a 3D model of the Earth's surface (typically ellipsoidal).

```{r}
# google earth - WGS84 (World Geodesic System 1984) lat-long
CRS("+init=epsg:4326")
```

```{r}
# US federal agencies - NAD83 (North American Datum 1983)
CRS("+init=epsg:4269")
```

### Projected

Easting/Northing for referencing location on 2D representations of the Earth's surface.

Example projections: Mercator, UTM, Robinson, Lambert, Sinusoidal, Robinson, Albers.

```{r}
# google maps, open street map
CRS("+init=epsg:3857")
```

```{r}
# OSGB36 (Ordnance Survey Great Britain 1936) easting / northing
CRS("+init=epsg:27700")
```

```{r}
# utm 30 (UK?)
CRS("+proj=utm +zone=30")
```

```{r}
# utm 48 (Cambidia?)
CRS("+proj=utm +zone=48")
```

https://www.rspatial.org/spatial/6-crs.html

https://www.nceas.ucsb.edu/~frazier/RSpatialGuides/OverviewCoordinateReferenceSystems.pdf

https://geocompr.robinlovelace.net/spatial-class.html#crs-intro

https://proj.org/

https://spatialreference.org

*********************************************************************

## SpatialPoints

```{r}
coords = cbind(x = c(0,0,1,1),
               y = c(0,1,0,1))
row.names(coords) = letters[1:4]
spoints = SpatialPoints(coords = coords, 
                        proj4string = CRS("+init=epsg:4227"))
```
```{r}
slotNames(spoints)
```
```{r}
spoints@coords
```
```{r}
spoints@bbox
```
```{r}
spoints@proj4string
```
```{r}
summary(spoints)
```
```{r}
plot(spoints, pch = 15, col = "blue", axes = FALSE)
```

### SpatialPointsDataFrame

```{r}
df = data.frame(z = 1:length(spoints))
row.names(df) = row.names(spoints)
spoints_df = SpatialPointsDataFrame(spoints, df)
spoints_df
```
```{r}
plot(spoints_df, 
     pch = spoints_df@data$z, 
     col = spoints_df@data$z, 
     axes = FALSE)
```

*********************************************************************

## SpatialLines

```{r}
L1 = Line(cbind(x = c(-1,-1,1,1), y = c(-1,1,1,-1)))
L2 = Line(cbind(x = c(-2,-2,2,2), y = c(-2,2,2,-2)))
Ls1 = Lines(list(L1), ID = "Ls1") # list can contain multiple Line objects
Ls2 = Lines(list(L2), ID = "Ls2") # list can contain multiple Line objects
slines = SpatialLines(LinesList = list(Ls1, Ls2), 
                      proj4string = CRS("+init=epsg:4227"))
```
```{r}
slotNames(slines)
```

Each `lines` object contains a list of `Lines` objects  

```{r}
str(slines@lines)
```
```{r}
slines@bbox
```
```{r}
slines@proj4string
```
```{r}
summary(slines)
```
```{r}
plot(slines, col = c("red", "blue"), axes = FALSE)
```

### Lines

```{r}
slotNames(slines@lines[[1]])
```

Each `Lines` object contains a list of `Line` objects

```{r}
str(slines@lines[[1]]@Lines)
```
```{r}
str(slines@lines[[1]]@ID)
```

### Line

```{r}
slotNames(slines@lines[[1]]@Lines[[1]])
```
```{r}
slines@lines[[1]]@Lines[[1]]@coords
```

### SpatialLinesDataFrame

```{r}
df = data.frame(z = 1:length(slines))
row.names(df) = row.names(slines)
slines_df = SpatialLinesDataFrame(slines, df)
str(slines_df)
```

*********************************************************************

## SpatialPolygons

```{r}
P1 = Polygon(cbind(x = c(-1,-1,1,1), y = c(-1,1,1,-1)))
P2 = Polygon(cbind(x = c(-2,-2,2,2), y = c(-2,2,2,-2)))
Ps1 = Polygons(list(P1), ID = "Ps1") # list can contain multiple Polygon objects
Ps2 = Polygons(list(P2), ID = "Ps2") # list can contain multiple Polygon objects
spoly = SpatialPolygons(Srl = list(Ps1, Ps2), 
                        pO = 2:1, 
                        proj4string = CRS("+init=epsg:4227"))
```
```{r}
slotNames(spoly)
```

Each `polygons` object contains a list of `Polygons` objects   

```{r}
str(spoly@polygons)
```
```{r}
spoly@plotOrder
```
```{r}
spoly@bbox
```
```{r}
spoly@proj4string
```
```{r}
summary(spoly)
```
```{r}
plot(spoly, col = 2:3, pbg = "white")
```

### Polygons

```{r}
slotNames(spoly@polygons[[1]])
```

Each `Polygons` object contains a list of `Polygon` objects

```{r}
str(spoly@polygons[[1]]@Polygons)
```
```{r}
spoly@polygons[[1]]@plotOrder
```

TODO: explain `labpt`

```{r}
spoly@polygons[[1]]@labpt
```
```{r}
spoly@polygons[[1]]@ID
```
```{r}
spoly@polygons[[1]]@area
```

### Polygon

```{r}
slotNames(spoly@polygons[[1]]@Polygons[[1]])
```
```{r}
str(spoly@polygons[[1]]@Polygons)
```

TODO: explain `labpt`

```{r}
spoly@polygons[[1]]@Polygons[[1]]@labpt
```
```{r}
spoly@polygons[[1]]@Polygons[[1]]@area
```

TODO: explain `hole`

```{r}
spoly@polygons[[1]]@Polygons[[1]]@hole
```
```{r}
spoly@polygons[[1]]@Polygons[[1]]@ringDir
```
```{r}
spoly@polygons[[1]]@Polygons[[1]]@coords
```

### SpatialPolygonsDataFrame

```{r}
```

*********************************************************************

## SpatialGridDataFrameand

TODO 

*********************************************************************

## SpatialPixelsDataFram

TODO 

*********************************************************************

## GridTopology

```{r}
sgrid <- GridTopology(c(0,0), c(1,1), c(10,10))
sgrid_poly <- as(sgrid, "SpatialPolygons")
plot(sgrid_poly, axes = TRUE)
text(coordinates(sgrid_poly), labels = row.names(sgrid_poly))
```

