---
title: sp
output: 
    github_document:
        toc: true
        toc_depth: 4
editor_options: 
  chunk_output_type: console
---

```{r knitr_config, include = FALSE}
source("_knitr_config.R")
library(sp)
```

******************************************************************************************

## CRS

* Coordinate Reference System  
* defines locations on the Earth's surface  
* notation used to describe the CRS is called the `proj4string` (from the `PROJ.4` library)  
* the proj4string has several attributes, including:
  * `proj` - projection
  * `datum` - defines origin and direction of axes
  * `ellps` - model for the shape of the earth
* CRS can also be reference by an EPSG code (European Petroleum Survey Group) 

### Geographic / unprojected

Latitude/longitde for referencing location on a 3D model of the Earth's surface (typically ellipsoidal).

```{r}
# google earth - WGS84 (World Geodesic System 1984) lat-long
CRS("+init=epsg:4326")
```

```{r}
# US federal agencies - NAD83 (North American Datum 1983)
CRS("+init=epsg:4269")
```

### Projected

Easting/Northing for referencing location on 2D representations of the Earth's surface.

Example projections: Mercator, UTM, Robinson, Lambert, Sinusoidal, Robinson, Albers.

```{r}
# google maps, open street map
CRS("+init=epsg:3857")
```

```{r}
# OSGB36 (Ordnance Survey Great Britain 1936) easting / northing
CRS("+init=epsg:27700")
```

```{r}
# utm 30 (UK?)
CRS("+proj=utm +zone=30")
```

```{r}
# utm 48 (Cambidia?)
CRS("+proj=utm +zone=48")
```

https://www.rspatial.org/spatial/6-crs.html

https://www.nceas.ucsb.edu/~frazier/RSpatialGuides/OverviewCoordinateReferenceSystems.pdf

https://geocompr.robinlovelace.net/spatial-class.html#crs-intro

https://proj.org/

https://spatialreference.org

******************************************************************************************

## SpatialPoints

S4 class with three slots:

* coords
* bbox
* proj4string

```{r}
coords = cbind(x = round(runif(10), 2), 
               y = round(runif(10), 2))
head(coords)
```
```{r}
spoints = SpatialPoints(coords)
spoints
```
```{r}
slotNames(spoints)
```
```{r}
spoints@coords
```
```{r}
spoints@bbox
```
```{r}
spoints@proj4string
```
```{r}
plot(spoints, pch = 2, axes = TRUE)
```

### SpatialPointsDataFrame

```{r}
df = data.frame(z = round(5 + rnorm(10), 2))
spoints_df = SpatialPointsDataFrame(spoints, df)
spoints_df
```

******************************************************************************************

## SpatialLines

```{r}
```

### SpatialLinesDataFrame

```{r}
```

******************************************************************************************

## SpatialPolygons

```{r}
Sr1 = Polygon(cbind(c(2,4,4,1,2),c(2,3,5,4,2)))
Sr2 = Polygon(cbind(c(5,4,2,5),c(2,3,2,2)))
Sr3 = Polygon(cbind(c(4,4,5,10,4),c(5,3,2,5,5)))
Sr4 = Polygon(cbind(c(5,6,6,5,5),c(4,4,3,3,4)), hole = TRUE)

Srs1 = Polygons(list(Sr1), "s1")
Srs2 = Polygons(list(Sr2), "s2")
Srs3 = Polygons(list(Sr3, Sr4), "s3/4")
SpP = SpatialPolygons(list(Srs1,Srs2,Srs3), 1:3)
plot(SpP, col = 1:3, pbg="white")

grd <- GridTopology(c(1,1), c(1,1), c(10,10))
polys <- as(grd, "SpatialPolygons")
plot(polys)
text(coordinates(polys), labels=row.names(polys))
```

### SpatialPolygonsDataFrame

```{r}
```

******************************************************************************************

SpatialGridDataFrameand
SpatialPixelsDataFram

